---
title: "README"
author: "Sergio H. S. de Quadros"
date: '2016-06-26'
output:
  html_document:
    fig_caption: yes
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
library(rmarkdown)
library(knitr)
library(xtable)
knitr::opts_chunk$set(echo = TRUE)
data("iris")
```

### Iris: Some advices for this _Shiny app_ and _RStudio presenter_ presentation

This (work)[https://sergioquadros.shinyapps.io/dev_data/] is simply an exercise about the shiny package and is not exhaustive nor shiny resources nor exploratory analysis. This homework was done for the course "Developing Data Products/Johns Hopkins University/Coursera" and consists of a shiny application and a presentation with the "RStudio Presenter".

We must select at first if you want a histogram or a scatter plot, both coulored by "Species", then:
 
1.   For the scatter plot you can choose 2 numeric variables and shall display it;

2.   For other one you can number of bins and shall display.

We tried by visual exploratory plotting to look for different distributions for each species at numeric variables.

We summarized the Edgar Anderson's Iris Data with 50 observations for each species - _I. setosa_, _I. versicolor_ and  _I. virginica_ - below:

```{r iris,echo=FALSE, results='asis'}
p <- summary(iris[,-5])
print(xtable(p), type = "html")
```


